### 2012-05-10 Rctl/inst/doc/manual.Rnw
[Rctl] Manual summary

\textbf{\sffamily Abstract}: Tutorial for the Correlated Trait Loci (CTL) mapping package to 
reconstruct genetic regulatory networks using the R package 'ctl' and the mapctl commandline 
tool. 
This tutorial is targetted at people with a basic understanding of genetics and would like to 
analyse there inbred cross or natural population. Main focus will be explaining the functionality 
of the software, and a how-to on loading datasets via Excel, tab delimited files (.csv) and 
R/qtl. In the methodology and background only a short introduction in CTL mapping theory is 
given.

>>>>

\textbf{\sffamily Abstract}: Tutorial for the Correlated Trait Loci (CTL) mapping package to 
reconstruct genetic regulatory networks using the R package 'ctl' and the mapctl commandline 
tool. 
This tutorial is targetted at people with a basic understanding of genetics and would like to 
analyse there inbred cross (RIL, DH, BC) or any population using SNP markers. Main focus will 
be explaining the functionality of the software, and a how-to on using datasets currently in 
Excel, tab delimited files (.csv) or use $read.cross$ from R/qtl. In the methodology and 
background only a short introduction in CTL mapping theory is given.
